---
title: "Pandoced revealjs pres 2018"
author: "Mac Dalmore"
date: "8 March 2018"
output:
  md_document:
    variant: markdown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Generate with Pandoc

## Pandoc sample

```{r sample, eval = FALSE, echo = TRUE}
% Pandoc command line (from presentation directory)
pandoc -t revealjs -s -o pandoc_pres.html pandoc_pres.md _pres.yaml -V revealjs-url=./reveal.js-3.6.0
```


# In the morning

## Getting up

- Turn off alarm
- Get out of bed

## Breakfast {data-background="#dddddd"}

- Eat eggs
- Drink coffee

# In the evening

## Dinner

- Eat spaghetti
- Drink wine

## Going to sleep

- Get in bed
- Count sheep

# Inclusion of R code

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

